---
title: "Estimation by method of moments."
author: "Chetana Jamadar"
date: "2023-01-03"
output: html_document
---

1. Generate a random sample of size n = 100 from Binomial distribution with parameters 
(n = 6,p = 0.86)Obtain method of moment estimates of n and p based on your sample.
```{r}
n=6
p=0.86
x=rbinom(100,n,p)
m=mean(x)
p_hat=m/n;p_hat
q_hat=1-p_hat;q_hat

```

2. Generate random sample of size n = 100 from Gamma distribution, with pdf is given by pdf is given
Take α = 7andβ = 4 Obtain method of moment estimates of αandβ based on your sample

```{r}
alpha=7;beta=4
x1=rgamma(100,alpha,1/beta);
m1=mean(x1)
m2=mean(x1^2)
v=var(x1)
beta_hat=v/m1;beta_hat
alpha_hat=m1/beta_hat;alpha_hat
```
3. consider a random sample of size n = 20 given below from Beta distribution of first kind with pdf
is
0.133904 0.224011 0.062282 0.122690 0.051213
0.620577 0.000650 0.271087 0.827109 0.929479
0.561905 0.160865 0.362565 0.001039 0.883135
0.393477 0.990179 0.045737 0.243155 0.080471
Obtain estimates of a,b based on your sample using method of moments.
```{r}
x1=c(0.133904,0.224011,0.062282,0.122690,0.051213,0.620577,0.000650,
0.271087,0.827109, 0.929479,0.561905,0.160865,0.362565,0.001039,
0.883135,0.393477,0.990179,0.045737,0.243155,0.080471)
m=mean(x1)
m1=mean(x1^2)
v=var(x1)
a_hat=m*(m-m1)/v;a_hat
b_hat=(1-m)*(m-m1)/v;b_hat
```
4. Generate a random sample of size n = 20 from truncated Poisson distribution, which is truncated
at point zero and obtained method of moment estimates of parameter θ based on your sample.
```{r}
n=20;
x=rpois(20,1)
X1=x/(1-exp(-1))
m1=mean(x1)
v1=var(x1)
l_hat=(v1+(m1^2))-m1/(m1);l_hat
```