---
title: "Unbiased estimator"
author: "Chetana Jamadar"
date: "2023-01-03"
output: html_document
---
1. Demonstrate the distribution of following statistics which is function of random sample from Poisson(λ =6)
(a) T1 = X
(b) T2 = S
2
Conclude that which one of the statistics is unbiased for parameterλ.Also compare both the statistics in terms of 
```{r}
rm(list=ls(all=TRUE))
l=6;
n=100;
for (i in 1:n)
{
x=matrix(c(rpois(n*n,l)),n,n);
T1=apply(x,2,mean);
T2=apply(x,2,var);
}
m1=mean(T1)
m2=mean(T2)
V1=var(T1);V1
V2=var(T2);V2
#Conclusion: Here, Var(T1)<var(T2) so,T1=X_bar is good
#estimator than T2=S^2
```
2. Demonstrate the distribution of following statistics which is based on random sample take from U(0,θ)
(a) T1 = X(n)
(b) T2 = 2X
Check that which one of the statistics is unbiased and which one has minimum variance.
```{r}
rm(list=ls(all=TRUE))
th=10;
n=100;
for (i in 1:n)
{
x=matrix(c(runif(n*n,0,th)),n,n);
T1=apply(x,2,max);
T2=2*apply(x,2,mean);
}
m1=mean(T1)
m2=mean(T2)
V1=var(T1);V1
V2=var(T2);V2

#Conclusion: T1=max(x) is biased estimator for theta and T2=2*mean(x)
#is unbiased estimator for theta.but T1 has minimum variance than T2.
```
3. Demonstrate the distribution of statistics which is based on random sample take fromB(n=7,p =0.45).CheckT1 = X/n is unbiased or not
```{r}
rm(list=ls(all=TRUE))
p=0.45;
n=100; #sample size
n1=7 #parameter
for (i in 1:n)
{
x=matrix(c(rbinom(n*n,n1,p)),n,n);
T1=(apply(x,2,mean))/n1;
}
m1=mean(T1)
V1=var(T1)
#Conclusion: T1 is unbiased estimator for P
```

