---
title: "Plotting power function"
author: "Chetana Jamadar"
date: "2023-01-03"
output: html_document
---
1. It is desired to test H0 : µ = 10 versus H1 : µ > 10on the basis of random sample of size n = 25 from
the normal population with unknown mean and variance σ
2 = 4.If the probability of type-I error
is to be α = 0.025 and the test function used is,
φ(x) =
½
1 i f x > c
0 o.w.
Where X = (X1,X2,...,X25) denote the random sample.
(a) Find the value of c.
(b) Find βφ(µ), Power function for µ = 10, 10.5, 11, 11.5, 12, 12.5, 13, 13.5, 14, 14.5, 15
(c) Plot the curve µ versus βφ(µ).
```{r}
mu=10;s_2=4
Za=qnorm(0.95,mu,sqrt(s_2),lower.tail=TRUE)
c=(Za*sqrt(s_2)+sqrt(n)*mu)/(sqrt(n))
x=rnorm(n,mu,sqrt(s_2))
m=mean(x)
mu1=c(10,10.5,11,11.5,12,12.5,13,13.5,14,14.5,15)
beta=rep(0,length(mu))
for (i in 1:length(mu1))
{
beta[i]=1-pnorm((15.56-mu1[i])*sqrt(n)/sqrt(s_2),
mu1[i],sqrt(s_2),lower.tail=1)
}
plot(mu1,beta,main="Power Functin Plot")

```
2. Suppose we want to test H0 : θ = 1 versus H1 : θ > 1 based on one observation from exponential
distribution with meanθ,Use the test function.
Find the power functionβφ(θ) = E(φ(x))and plot the θ versusβφ(θ)
```{r}
n=1;Theta=1
x=rexp(n,Theta)
theta=seq(1,10,0.5)
for(i in 1:length(theta))
{
beta[i]=(1-pexp(2,theta[i]))+0.8*dexp(2,theta[i])
}
plot(theta,beta,main="Power Function plot")

```

