---
title: "Most Powerful Test"
author: "Chetana Jamadar"
date: "2023-01-03"
output: html_document
---
1. Develop MP test for testing H0 : λ = λ0 versus H0 : λ = λ1 (λ1 > λ0)based on a random sample of
size n = 30 from a Poisson(λ) with α = 0.05.Find Power of your test. Generate a random sample of
size n = 30 from Poisson(λ) withλ = 2 and based on this sample give your decision about acceptance or rejection of H0 for testing H0 : λ = 2 versus H0 : λ = 4 with α = 0.05using test given by you
```{r}
l0=2;c=73
g=(0.05-1+ppois(c,60))/dpois(c,60);g
x=rpois(30,2)
X1=sum(x);X1
pow=1-ppois(73,120)+0.4627*dpois(73,120);pow
#Conclusion: Here sum(x) is less than 73 so there
#is no evidence to reject Ho
```
2. Develop MP test for testing H0 : P = P0 versusH0 : P = P1 (P1 > P0)based on a random sample of
size n = 25 from a Bernoulli(P) with α = 0.1.Find Power of your test. A random sample of size
n = 25from Bernoulli(P) are given and based on this sample give your decision about acceptance
or rejection of H0 for testing H0 : P = 0.5 versusH0 : P = 0.7 with α = 0.1using test given by you. 1 0
1 0 0 0 0 0 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 1
```{r}
p0=0.5;c=16
g=(0.1-1+pbinom(c,25,0.5))/dbinom(c,25,0.5);g
x=c(1,0,1,0,0,0,0,0,0,1,0,0,1,1,0,1,1,0,0,0,1,1,0,0,1)
sum(x)
pow=1-pbinom(16,25,0.7)+0.7575*dbinom(16,25,0.7);pow
#Conclusion: Here sum(x) is less than 16 so there
#is no evidence to reject Ho

```
